\documentclass{article}

\title{Dramatis Personae}

\begin{document}

\maketitle

\section*{Employee: Brandon Greathouse}

\subsection{Motivation}

Wants a job for the \$\$\$.
Has friends who have worked as baristas in coffee shops.

\subsection{Details}

\begin{description}
    \item[Studying.]
        At McGill, majoring political science. He studies in the library, not
        in his dorm, since it'd distracting. Conclusion: he cares about school.

    \item[Age.] 18 years old.

    \item[Where?]
        Lives in RVC.

    \item[Musical tastes.]
        Listens mostly to pop. Doesn't like EDM, but listens to it when he's
        with his friends since they like it.

    \item[Parents.]
        Middle income. Parents still together.

    \item[Long-term goal.]
        Wants to work as a journalist for \emph{The Economist}.

    \item[Physical characteristics.]
        Weighs $65$~kg. Has short brown wavy hair. Five feet and eight inches
        tall, with a slim physique.

    \item[Hometown.]
        Ottawa.

    \item[Dog.]
        Had a Labrador back at home.

    \item[Relationship status.]
        Got his first girlfriend a few weeks ago. He's pretty serious about
        her, but she's not really into it.

    \item[Hobbies.]
        Plays intramural soccer. Watches John Oliver.
\end{description}

\section{Employer: Rupert Chase}

\subsection{Details}

\begin{description}
    \item[Age.]
        35 years old.

    \item[Alma mater.]
        Psychology major from Universit\'e de Montr\'eal, but doesn't want to
        do stuff related to his degree.

    \item[Coffee shop.]
        Coffee is fair trade, ground by hand, and roasted on location. He's
        passionate about coffee. Likes chatting with customers and want
        sociable employees. Pays himself a reasonable salary.  Wants the shop
        to be the most famous in the city: put Montreal on the map because of
        him. Wants to be featured on Tripadvisor.

    \item[Social media.]
        Loves social media: has accounts for his shop on Twitter and Facebook. Cares a lot about Yelp and Urbanspin ratings.

    \item[Home life.]
        Lives with asian girlfriend in 1-bedroom studio apartment.

    \item[Political opinions.]
        Parti Qu\'eb\'ecois.

    \item[Physical characteristics.]
        White, bearded, lanky.

    \item[Dress.]
        Flannel shirt, skinny jeans, designer boots.

    \item[Hiring process.]
        Hires people by posting ads on Kijiji and Craigslist.

    \item[Miscellaneous.]
        He's a hipster: uses an iPhone and a MacBook Air. Does his finances on
        Quickbooks. Likes new gadgets. Used to play guitar in high school, but
        isn't very good at it anymore.
\end{description}

\end{document}
